Concurrent Programming in Harmony

### 2022-01-23 book/paper.tex
Removed installation instructions from book

If you already know about concurrent and distributed programming and
are just interested in a ``speed course'' on Harmony, I would recommend
reading \autoref{ch:harmonyintro}, \autoref{ch:harmonymachine},
\autoref{ch:method}, \autoref{ch:specification}, and \autoref{ch:cds}.
The appendices contain various details about Harmony itself, including
an appendix on convenient Harmony modules (\autoref{ap:module}),
an appendix that explains how Harmony works (\autoref{ap:howitworks}),
and
an appendix on installing and running Harmony (\autoref{ap:install}).

@@

Harmony, too, has a Hello World program.
\autoref{fig:helloworld} shows the program and the corresponding output.
From the command line, you can run it as follows:
\begin{code}
\begin{verbatim}
$ harmony -o hello1.png code/hello1.hny
\end{verbatim}
\end{code}
For this to work, make sure \texttt{harmony} is in your command shell's
search path.
The code for examples in this book can be found in the \texttt{code}
folder under the name listed in the caption of the example.
In this case, the file \texttt{code/hello1.hny} contains the
code in \autoref{fig:helloworld}.
The \texttt{-o hello1.png} arguments tell harmony to write the output
in the file \texttt{hello1.png}.
The output is a \emph{Deterministic State Machine} (DFA).  The green circle
represents the initial state and the double circle represents the final
state.  There is one \emph{transition}, labeled with the string
``hello world''.  The DFA describes (or \emph{recognizes}) all possible
outputs that the program can generate.  In this case, there is only one.

@@

\chapter{Installing and Running Harmony}\label{ap:install}

@@

\texttt{Harmony IDE} is an Integrated Development Environment for Harmony,
also developed by Kevin Sun and Anthony Yang,
that runs in the cloud.  An important advantage of using \texttt{Harmony IDE}
is that you do not have to install anything.  You can even run in on your
smartphone.  However, since Harmony programs can use significant compute
resources, \texttt{Harmony IDE} must put a limit on the amount of compute
resources you can use.  So, while \texttt{Harmony IDE} is currently a great
way to try out Harmony, if you become a serious user of Harmony you
will probably want to install either the command-line version or
\texttt{HarmonyLang}.

>>>>

If you already know about concurrent and distributed programming and
are just interested in a ``speed course'' on Harmony, I would recommend
reading \autoref{ch:harmonyintro}, \autoref{ch:harmonymachine},
\autoref{ch:method}, \autoref{ch:specification}, and \autoref{ch:cds}.
The appendices contain various details about Harmony itself, including
an appendix on convenient Harmony modules (\autoref{ap:module}),
and an appendix that explains how Harmony works (\autoref{ap:howitworks}),

@@

Harmony, too, has a Hello World program.
\autoref{fig:helloworld} shows the program and the corresponding output.
After installation (see \url{https://harmony.cs.cornell.edu}), you
can run it as follows from the command line:
\begin{code}
\begin{verbatim}
$ harmony -o hello1.png code/hello1.hny
\end{verbatim}
\end{code}
For this to work, make sure \texttt{harmony} is in your command shell's
search path.
The code for examples in this book can be found in the \texttt{code}
folder under the name listed in the caption of the example.
If you need to, you can download the sources separately from
\url{https://harmony.cs.cornell.edu/sources.zip}.
In this case, the file \texttt{code/hello1.hny} contains the
code in \autoref{fig:helloworld}.
The \texttt{-o hello1.png} arguments tell harmony to write the output
in the file \texttt{hello1.png}.
The output is a \emph{Deterministic State Machine} (DFA).  The green circle
represents the initial state and the double circle represents the final
state.  There is one \emph{transition}, labeled with the string
``hello world''.  The DFA describes (or \emph{recognizes}) all possible
outputs that the program can generate.  In this case, there is only one.

@@

\begin{comment}
\chapter{Installing and Running Harmony}\label{ap:install}

@@

\texttt{Harmony IDE} is an Integrated Development Environment for Harmony,
also developed by Kevin Sun and Anthony Yang,
that runs in the cloud.  An important advantage of using \texttt{Harmony IDE}
is that you do not have to install anything.  You can even run in on your
smartphone.  However, since Harmony programs can use significant compute
resources, \texttt{Harmony IDE} must put a limit on the amount of compute
resources you can use.  So, while \texttt{Harmony IDE} is currently a great
way to try out Harmony, if you become a serious user of Harmony you
will probably want to install either the command-line version or
\texttt{HarmonyLang}.
\end{comment}
